MachLensFinder - I: An automated Strong Lensing Identification Pipeline

### 2016-12-23 ms.tex
Added a caption for the LSST-like images

% Defining the 6 paradigms of classification
In this section, we discuss the different image types that our model
is most and least able to successfully classify.  We have six
paradigms of model performance on the mock images, and include a
larger compilation of each of the six image classification paradigms
in the Appendix for the various models we have trained.

@@

\caption{LSST-like images with a BCG. These illustrate the same image
  classification paradigms as Figure~\ref{fig:HSTclassificationtile}.}
\label{fig:LSSTBCGclassificationtile}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% Defining the 6 paradigms of classification
In this section, we discuss the different image types that our model
is most and least able to successfully classify.  We have six
paradigms of model performance on the mock images, \todo{and include a
larger compilation of each of the six image classification paradigms
in the Appendix for the various models we have trained}.

@@

\caption{LSST-like images with a BCG. These illustrate the same image
  classification paradigms as Figure~\ref{fig:HSTclassificationtile}.
  Note, the larger PSF of LSST reduces the resolution of images,
  making the arc-like morphology of faint images less significant and
  increases the appearance of image-BCG blending.}
\label{fig:LSSTBCGclassificationtile}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
